Curriculum and Imitation Learning for Bipedal Locomotion on Rough Terrain

### 2019-02-02 paper/rss/main.tex
Add doppelganger for 2D environment
This is mostly to make it easier to hack together a diagram of the FSM.

Also tweak training settings for 3D; trying to run official 3D experiments
now.

Using the TG and learning algorithm described in Sec. \ref{sec:approach} above, our HLP is able to achieve reward $A\pm B$ (one standard deviation) after only $C$ simulated training footsteps.
\nhatch{Put actual numbers here.}
Examples of the final policies may be seen in the supplemental video.
To the best of our knowledge, our approach is the first to achieve such precise foot placement
using a fast, dynamic gait that requires no optimization during policy execution.

@@

In particular, CIM is an intriguing direction for bipedal locomotion research.
To the best of our knowledge, our experiments are the first to achieve such precise foot placement
using a fast, dynamic gait that requires no optimization during policy execution.
However, one significant limitation of our work so far is that all experiments were performed in simulation.
In future work, we plan to investigate how to transfer policies trained with CIM to real-world bipedal robots.
We also plan to investigate whether it helps to have an \emph{adaptive} curriculum that adjusts to the learner's current ability.

>>>>

Using the TG and learning algorithm described in Sec. \ref{sec:approach} above, our HLP is able to achieve reward $A\pm B$ (one standard deviation) after only $C$ simulated training footsteps.
\nhatch{Put actual numbers here.}
Examples of the final policies may be seen in the supplemental video.
To the best of our knowledge, our approach is the first to achieve such precise foot placement
using a fast, non-static gait that requires no optimization during policy execution.

@@

In particular, CIM is an intriguing direction for bipedal locomotion research.
To the best of our knowledge, our experiments are the first to achieve such precise foot placement
using a fast, non-static gait that requires no optimization during policy execution.
However, one significant limitation of our work so far is that all experiments were performed in simulation.
In future work, we plan to investigate how to transfer policies trained with CIM to real-world bipedal robots.
We also plan to investigate whether it helps to have an \emph{adaptive} curriculum that adjusts to the learner's current ability.
